GPU Efficient Texture Based Bezier Curve Evaluation

### 2015-06-29 Paper/paper.tex
3d texture wip

Three dimensional textures (often refered to as volumetric textures) are textures which are MxNxO pixels in size such as 8x8x2 or 16x8x4.

Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions.

@@

TODO: flesh out details, show diagram of texture layout.
TODO: GLSL for cubic and quartic, but images for cubic, quartic with comparison vs ground truth.
TODO: explain how linear and quadratic could still be achieved even if it isn't that useful (ye? Hw/sw)
TODO: beyond 3d textures? Could do 4d with mipmapped volumetric textures!

@@

TODO: dimensionality / curve order comparisons. A table? Maybe side by side images?
TODO: texture size changes, number of textures used, number of texture samples taken
TODO: include quadrilinear and above?
TODO: we might want to do this in the performance results section instead and provide perf metrics as well.

>>>>

Three dimensional textures (often refered to as volumetric textures) are textures which are $(W,H,D)$ pixels in size such as $(8,8,2)$ or $(16,8,4)$.

Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions (\autoref{fig:decdimensionality}).

@@

You may have noticed that a 1d texture can store a linear curve, but that a 2d texture cannot.  The lowest order curve it can store is a quadratic curve.  In the case of a 3d texture, the minimum goes up again, and the lowest order curve you can store is a cubic curve.

TODO: formula for texture size

\begin{figure}
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-2,0);
      \draw (0.5,-0.5) node {$A$};
      \draw (1.5,-0.5) node {$B$};
      \draw (0.5,-1.5) node {$B$};
      \draw (1.5,-1.5) node {$C$};

      \begin{scope}[shift={(0.75,0.75,0)}]
        \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-2,0);
        \draw[gray] (0.5,-0.5) node {$B$};
        \draw[gray] (1.5,-0.5) node {$C$};
        \draw[gray] (0.5,-1.5) node {$C$};
        \draw[gray] (1.5,-1.5) node {$D$};
      \end{scope}

      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
      \draw[dashed] (2,0,0) -- (2.75, 0.75,0);
      \draw[dashed] (0,-2,0) -- (0.75,-1.25,0);
      \draw[dashed] (2,-2,0) -- (2.75,-1.25,0);
    \end{tikzpicture}
    \hspace{5mm}
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-2,0);
      \draw (0.5,-0.5) node {$A$};
      \draw (1.5,-0.5) node {$B$};
      \draw (0.5,-1.5) node {$B$};
      \draw (1.5,-1.5) node {$C$};

      \draw (2.5,-0.5) node {$E$};
      \draw (3.5,-0.5) node {$F$};
      \draw (2.5,-1.5) node {$F$};
      \draw (3.5,-1.5) node {$G$};

      \begin{scope}[shift={(0.75,0.75,0)}]
        \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-2,0);
        \draw[gray] (0.5,-0.5) node {$B$};
        \draw[gray] (1.5,-0.5) node {$C$};
        \draw[gray] (0.5,-1.5) node {$C$};
        \draw[gray] (1.5,-1.5) node {$D$};

        \draw[gray] (2.5,-0.5) node {$F$};
        \draw[gray] (3.5,-0.5) node {$G$};
        \draw[gray] (2.5,-1.5) node {$G$};
        \draw[gray] (3.5,-1.5) node {$H$};
      \end{scope}

      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
      \draw[dashed] (4,0,0) -- (4.75, 0.75,0);
      \draw[dashed] (0,-2,0) -- (0.75,-1.25,0);
      \draw[dashed] (4,-2,0) -- (4.75,-1.25,0);
    \end{tikzpicture}

    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-3,0);
      \draw (0.5,-0.5) node {$A$};
      \draw (1.5,-0.5) node {$B$};
      \draw (0.5,-1.5) node {$B$};
      \draw (1.5,-1.5) node {$C$};
      \draw (0.5,-2.5) node {$C$};
      \draw (1.5,-2.5) node {$D$};

      \begin{scope}[shift={(0.75,0.75,0)}]
        \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-3,0);
        \draw[gray] (0.5,-0.5) node {$B$};
        \draw[gray] (1.5,-0.5) node {$C$};
        \draw[gray] (0.5,-1.5) node {$C$};
        \draw[gray] (1.5,-1.5) node {$D$};
        \draw[gray] (0.5,-2.5) node {$D$};
        \draw[gray] (1.5,-2.5) node {$E$};
      \end{scope}

      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
      \draw[dashed] (2,0,0) -- (2.75, 0.75,0);
      \draw[dashed] (0,-3,0) -- (0.75,-2.25,0);
      \draw[dashed] (2,-3,0) -- (2.75,-2.25,0);
    \end{tikzpicture}
    \hspace{5mm}
    \begin{tikzpicture}
      \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-3,0);
      \draw (0.5,-0.5) node {$A$};
      \draw (1.5,-0.5) node {$B$};
      \draw (0.5,-1.5) node {$B$};
      \draw (1.5,-1.5) node {$C$};
      \draw (0.5,-2.5) node {$C$};
      \draw (1.5,-2.5) node {$D$};

      \draw (2.5,-0.5) node {$F$};
      \draw (3.5,-0.5) node {$G$};
      \draw (2.5,-1.5) node {$G$};
      \draw (3.5,-1.5) node {$H$};
      \draw (2.5,-2.5) node {$H$};
      \draw (3.5,-2.5) node {$I$};

      \begin{scope}[shift={(0.75,0.75,0)}]
        \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-3,0);
        \draw[gray] (0.5,-0.5) node {$B$};
        \draw[gray] (1.5,-0.5) node {$C$};
        \draw[gray] (0.5,-1.5) node {$C$};
        \draw[gray] (1.5,-1.5) node {$D$};
        \draw[gray] (0.5,-2.5) node {$D$};
        \draw[gray] (1.5,-2.5) node {$E$};

        \draw[gray] (2.5,-0.5) node {$G$};
        \draw[gray] (3.5,-0.5) node {$H$};
        \draw[gray] (2.5,-1.5) node {$H$};
        \draw[gray] (3.5,-1.5) node {$I$};
        \draw[gray] (2.5,-2.5) node {$I$};
        \draw[gray] (3.5,-2.5) node {$J$};
      \end{scope}

      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
      \draw[dashed] (4,0,0) -- (4.75, 0.75,0);
      \draw[dashed] (0,-3,0) -- (0.75,-2.25,0);
      \draw[dashed] (4,-3,0) -- (4.75,-2.25,0);
    \end{tikzpicture}

    \caption{\textit{Top Left:} A cubic curve encoded in a $(2,2,2)$ sized texture, decoded with a single trilinear texture sample. \textit{Top Right:}  Two piecewise cubic curves encoded in a $(4,2,2)$ sized texture, decoded with a single trilinear texture sample.  \textit{Bottom Left:} A Quartic curve encoded in a $(2,3,2)$ sized texture, decoded with two trilinear texture samples. \textit{Bottom Right:} Two piecewise quartic curves encoded in a $(4,3,2)$ sized texture, decoded with two trilinear texture samples.} 
    \label{fig:texlayeout1d}
  \end{figure}

TODO: GLSL for cubic!

@@

TODO: dimensionality / curve order comparisons. A table? Maybe side by side images?
TODO: texture size changes, number of textures used, number of texture samples taken
TODO: include quadrilinear and above?
TODO: we might want to do this in the performance results section instead and provide perf metrics as well.
TODO: beyond 3d textures?
